POMDP comparisons across sigma_m, sigma_g

### 2018-01-30 appendix/appendix_recruit_first.Rmd
namespace

pomdp_policies <- df %>% 
  select(-value) %>% 
  rename(uniform = policy) %>% 
  gather(policy, harvest, -state) %>%
  mutate(state = states[state], 
         harvest = actions[harvest]) %>%
  mutate(escapement = f(state,harvest)) %>%
  select(state, policy, harvest, escapement)

>>>>

pomdp_policies <- df %>% 
  select(-value) %>% 
  dplyr::rename(uniform = policy) %>% 
  gather(policy, harvest, -state) %>%
  mutate(state = states[state], 
         harvest = actions[harvest]) %>%
  mutate(escapement = f(state,harvest)) %>%
  select(state, policy, harvest, escapement)
